Data Cleaning

### 2025-12-10 Data Cleaning.Rmd
Edited table display for confusion matrices.

```{r, include=F}
library(ISLR) ## data package
library(tidyverse) ## data manipulation
library(tidymodels) ## tidy modeling
library(knitr) ## tables
library(rpart.plot) ## tree diagrams
library(vip) ## plotting variable importance
library(dplyr)
library(tidyr)
library(readr)
library(lubridate)
library(ggplot2)
library(zoo)
library(purrr)
library(knitr)
library(patchwork) ## plot arrangement
library(parsnip)
library(discrim)
library(nnet)
library(broom)
library(dplyr)
library(kableExtra)

@@

# results
print(accuracy_result)
print(confusion_matrix)

>>>>

```{r, include=F}
library(ISLR) ## data package
library(tidyverse) ## data manipulation
library(tidymodels) ## tidy modeling
library(knitr) ## tables
library(rpart.plot) ## tree diagrams
library(vip) ## plotting variable importance
library(dplyr)
library(tidyr)
library(readr)
library(lubridate)
library(ggplot2)
library(zoo)
library(purrr)
library(knitr)
library(patchwork) ## plot arrangement
library(parsnip)
library(discrim)
library(nnet)
library(broom)
library(dplyr)
library(kableExtra)
library(tibble)

@@

# results
print(accuracy_result)
print(confusion_matrix) |> kable()
